Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-30 docs/paper/paper.Rmd
add relative scoring

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = FALSE,
  message = FALSE
)
```

@@

```{r packages}
library(data.table)
library(ggplot2)
library(scales)
library(lemon)
library(here)
```

@@

@@

- Figure 1:
  - X: date
  - Y: incidence rate
  - Colour: Model
  - X facet: Country
  - Y facet: Horizon

```{r vis-forecasts}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

forecasts[location_name %in% locs] |>
  DT(, date := target_end_date) |>
    plot_predictions(
      by = c("horizon", "location_name"), range = c(30, 60, 90)
    ) +
    facet_grid(
      location_name ~ horizon) +
    aes(fill = model, col = model) +
    scale_y_log10(labels = comma, oob = squish, limits = c(0.1, 1000)) +
    scale_fill_brewer(palette = "Dark2") +
    scale_color_brewer(palette = "Dark2") +
    labs(x = "Date", fill = "Model", col = "Model", ramp = "Range",
         y = "Notified test positive cases per 10,000 population")
```

@@

# Discussion {-}

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  cache = TRUE
)
```

@@

```{r packages}
library(data.table)
library(scoringutils)
library(ggplot2)
library(scales)
library(here)
```

@@

```{r coverage}
ranges <- c(30, 60, 90)

coverage <- scores |>
  copy() |>
  DT(, horizon := as.character(horizon)) |>
  DT(, coverage_deviation := NULL) |>
  add_coverage(ranges = ranges, by = c("model", "horizon")) |>
  summarise_scores(fun = signif, digits = 2, by = c("model", "horizon")) |>
  melt(
    measure.vars = patterns("coverage_"), variable.name = "range",
    value.name = "coverage"
  )|>
  DT(, range := gsub("coverage_", "", range)) |>
  DT(, range := paste0(range, "% interval"))
```

```{r relative-interval-score}
relative_interval_score <- scores |>
  copy() |>
  setorderv(c(
    "location", "target_end_date", "horizon", "quantile", "model"
  )) |>
  DT(,
    relative_interval_score := interval_score / shift(interval_score),
    by = c("location", "target_end_date", "horizon", "quantile")
  ) |>
  DT(model %in% "Surrogate")
```

@@

```{r vis-forecasts, fig.height = 9, fig.width = 9, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30%, 60%, and 90% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time."}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

forecasts[location_name %in% locs] |>
  DT(, date := target_end_date) |>
  plot_predictions(
    by = c("horizon", "location_name"), range = c(30, 60, 90)
  ) +
  facet_grid(
    location_name ~ horizon, scales = "free_y"
  ) +
  aes(fill = model, col = model) +
  scale_y_log10(labels = comma, oob = squish, limits = c(NA, NA)) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(x = "Date", fill = "Model", col = "Model", ramp = "Range",
        y = "Notified test positive cases per 10,000 population")
```

@@

```{r plot-coverage}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

plot_cov_levels <- ggplot(coverage) +
  aes(
    x = horizon, y = coverage, colour = model, group = interaction(range, model)
  ) +
  geom_line() +
  geom_point() +
  geom_hline(
    data = hlines, aes(yintercept = nominal, x = NULL), linetype = "dashed"
  ) +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels = percent) +
  facet_wrap(vars(range), ncol = 1) +
  theme_scoringutils() +
  labs(
     y = "Proportion of data within forecast interval",
     x = "Forecast horizon (weeks)",
     col = "Model"
  )

plot_cov_quantile <- scores |>
  summarise_scores(by = c("model", "quantile", "horizon")) |>
  plot_quantile_coverage(scores) +
  aes(col = model) +
  scale_colour_brewer(palette = "Dark2") +
  facet_wrap(vars(horizon)) +
  labs(col = "Model")

plot_interval_score <- relative_interval_score |>
  geom
```
# Discussion {-}
